# Introduction
The standard of living became more and more important for the world population. But every standard of living comes at a price. How high the standard of living is in a country can be analyzed and compared between countries with the help of the cost of living index.

## Task description
Our task was to analyze a data set and write a report about it using R, RStudio, RMarkdown and the procedures of literate programming to put together a PDF-manuscript.
In our team we have received the "cost of living" data set and analyzed it with the research question "Is there a significant difference between industrialized countries and developing countries in cost of living?"

## Structure
Our document is divided into five chapters. This chapter is the introduction, where we describe the task and how we imported our dataset, respectively added other datasets. 
In the chapter "Theoretical Background" the theoretical background of the dataset and the data collection is briefly discussed, before in the methods section the dataset is statistically described, including information on the variables’ distribution, missing values,
categories and the relationships between the variables.
The results section comprise all necessary calculations, which are then discussed in connection with the research question in the following section ("Discussion").

## Setup
After the required libraries, which will be worked with in the following, were installed, the libraries still had to be imported in order to be able to use them.

```{r}
#| message = FALSE,
#| warning = FALSE
library(tidyverse)
library(dplyr)
library(stringr)
library(ggplot2)
library(maps)
library(janitor)
library(modelsummary)
library(car)
library(carData)
library(gpairs)
library(GGally)
```

Subsequently, the data had to be read in. This could be initialized with the following command, after the data set was added as a csv file in the folder "02-data".
To be able to work better with the names of the columns and the dataset in general, the command "janitor::clean_names" was executed.  With this, for example, the spaces were removed and the names were all written in small letters.

```{r}
#| message = FALSE,
#| warning = FALSE
costOfLiving <- read_delim("02-data/cost-of-living-2017.csv", 
                      delim = "\t", escape_double = FALSE, 
                      trim_ws = TRUE)
costOfLiving <- janitor::clean_names(costOfLiving)
```

To make it easier to split the data by region, we imported a csv file that shows the names of the countries in this world and their corresponding regions.

First we had to import the dataset, which we named "continents". This dataset is from the website "kaggle", named "Country Mapping - ISO, Continent, Region". ^[@continents2]

```{r}
#| message = FALSE,
#| warning = FALSE
#import list of continents and countries
continents <- read_csv("02-data/continents2.csv")
continents <- janitor::clean_names(continents)
```

To be able to do a join with the raw data, we had to rename the column "name" to "country". After that, a left join could be performed on the renamed column. Since we only needed the column "region", a select for this one column was performed within the join.

```{r}
#| message = FALSE,
#| warning = FALSE
#rename attribute 'name' in 'country' to perform a left join.
continents <- rename(continents, country = name)
costOfLivingAndContinents <- left_join(costOfLiving, select(continents, country, region), by="country")
```

Now it was possible to check if a country was not assigned to a region. 
Since the country Kosovo could not be assigned to a region, this had to be done manually.

```{r}
#| message = FALSE,
#| warning = FALSE
costOfLivingAndContinents[486, 12] <- "Europe"
```

To assign the different countries in our dataset to either a developing or an industrialized country, we also imported a new csv file, which we named "dd". 
We created this file ourselves, based on data from @ddcountries.

```{r}
#| message = FALSE,
#| warning = FALSE
#import list of Countries and development status
dd <- read_delim("02-data/developed_and_developing_countries.csv",
                 delim = ";", escape_double = FALSE,
                 trim_ws = TRUE)
dd <- janitor::clean_names(dd)
```

To format the category as a double value, we executed the following commands.

```{r}
#| message = FALSE,
#| warning = FALSE
dd$category[dd$category == "developed"] <- 1.0
dd$category[dd$category == "developing"] <- 0.0
dd$category <- as.double(dd$category)
```

Once this was done, we scanned the dataset for various capitalization errors and corrected them. Also we have renamed the column category to development.

```{r}
#| message = FALSE,
#| warning = FALSE
dd$country[dd$country == "italy"] <- "Italy"
dd$country[dd$country == "Hong Kong SAR"] <- "Hong Kong"
dd$country[dd$country == "Taiwan Province of China"] <- "Taiwan"
dd$country[dd$country == "Russian Federation"] <- "Russia"
dd$country[dd$country == "Viet Nam"] <- "Vietnam"
dd$country[dd$country == "Bosnia and Herzegovina"] <- "Bosnia And Herzegovina"
dd$country[dd$country == "Kosovo"] <- "Kosovo (Disputed Territory)"
colnames(dd)[2] <- "development"
```

In the end, we were able to perform a left join and thus add the categorization of development countries to our dataset.

```{r}
#| message = FALSE,
#| warning = FALSE
dataFinished <- left_join(costOfLivingAndContinents,dd, by="country")
```