# Introduction

kurze Einleitung über die Aufgabenstellung (ggf. die Rollen und Aufgabenverteilung im Team)

- Was wurde gemacht?
- Beschreibung der einzelnen Kapitel
- Kurze Beschreibung der Thematik
- code junk mit libary und daten

The standard of living became more and more important for the world population. But every standard of living comes at a price. How high the standard of living is in a country can be analyzed and compared between countries with the help of the cost of living index.

## Setup
After the required libraries, which will be worked with in the following, were installed, the libraries still had to be imported in order to be able to use them.

```{r}
library(tidyverse)
library(dplyr)
library(stringr)
library(ggplot2)
library(maps)
library(janitor)
library(modelsummary)
library(car)
library(carData)
library(gpairs)
library(GGally)
```

Subsequently, the data had to be read in. This could be initialized with the following command, after the data set was added as a csv file in the folder "02-data".
To be able to work better with the names of the columns and the dataset in general, the command "janitor::clean_names" was executed.  With this, for example, the spaces were removed and the names were all written in small letters.

```{r}
costOfLiving <- read_delim("02-data/cost-of-living-2017.csv", 
                      delim = "\t", escape_double = FALSE, 
                      trim_ws = TRUE)
costOfLiving <- janitor::clean_names(costOfLiving)
```

To make it easier to split the data by region, we imported a csv file that shows the names of the countries in this world and their corresponding regions.

First we had to import the dataset, which we named "continents".

```{r}
#import list of continents and countries
continents <- read_csv("02-data/continents2.csv")
continents <- janitor::clean_names(continents)
```

To be able to do a join with the raw data, we had to rename the column "name" to "country". After that, a left join could be performed on the renamed column. Since we only needed the column "region", a select for this one column was performed within the join.

```{r}
#rename attribute 'name' in 'country' to perform a left join.
continents <- rename(continents, country = name)
costOfLivingAndContinents <- left_join(costOfLiving, select(continents, country, region), by="country")
```

Now it was possible to check if a country was not assigned to a region. 

```{r}
filter(costOfLivingAndContinents, is.na(region))
```

Since the country Kosovo could not be assigned to a region, this had to be done manually.

```{r}
costOfLivingAndContinents[486, 12] <- "Europe"
```

TODO

```{r}
#import list of Countries and development status
dd <- read_delim("02-data/developed_and_developing_countries.csv",
                 delim = ";", escape_double = FALSE,
                 trim_ws = TRUE)
dd <- janitor::clean_names(dd)
dd$category[dd$category == "developed"] <- 1.0
dd$category[dd$category == "developing"] <- 0.0
dd$category <- as.double(dd$category)


dd$country[dd$country == "italy"] <- "Italy"
dd$country[dd$country == "Hong Kong SAR"] <- "Hong Kong"
dd$country[dd$country == "Taiwan Province of China"] <- "Taiwan"
dd$country[dd$country == "Russian Federation"] <- "Russia"
dd$country[dd$country == "Viet Nam"] <- "Vietnam"
dd$country[dd$country == "Bosnia and Herzegovina"] <- "Bosnia And Herzegovina"
dd$country[dd$country == "Kosovo"] <- "Kosovo (Disputed Territory)"
colnames(dd)[2] <- "development"

dataWithCategory <- left_join(costOfLivingAndContinents,dd, by="country")
dataWithCategory
````