---
output:
  pdf_document: default
  html_document: default
---
# Methods

## Exploratory Data Analysis

First of all, we had to check, if there are missing values inside of the data-set. Therefore we used the following code to proof this:

```{r}
#| echo = TRUE,
#| message = TRUE
summary(is.na(dataWithCategory))
```
As it can be seen, there were $`r sum(is.na(dataWithCategory$state))`$ missing values inside the column "state". 
However, since the column has no bearing on our research question, we decided to disregard this column. With the city column we have a more meaningful basis to answer our question.
To disregard this column, we cut it off. To do this, we used to following R code chunk. Because it is the second column, we can just delete this column.

```{r}
#| echo = TRUE,
#| message = TRUE
dataWithCategory <- dataWithCategory[-2]
```

We also truncated the leverage_model_1 and leverage_model_2 columns, since we did not work with these columns any further.

```{r}
#| echo = TRUE,
#| message = TRUE
dataWithCategory <- dataWithCategory[-9]
dataWithCategory <- dataWithCategory[-9]
```


## Folgendes nur zur Übersicht/weiteren Aufbau(Gliederung)

zu wrangling gehören joining, merging und grouping
Boxplot gehört zu profiling

3. Methods, for example:
- Descriptive statistics
- Variable distributions
- Statements about variances and co-variance and missing values
- Chosen analytical procedures to answer the research question


Inhalt/Aufbau:
  1:EDA (Exploratory Data Analysis) auf Datenset    anwenden
    1.1: including information on the variables’ distribution, missing values,
categories / grouping factors (if applicable) and the relationships between the variables, especially
regarding the variable in focus, for example, the dependent variable of a applied statistical method (if
applicable)
  2:Methoden/statistische Modelle aufstellen