---
output:
  pdf_document: default
  html_document: default
---
# Methods

## Data Description
```{r}
#| message = FALSE,
#| warning = FALSE,
#| echo = FALSE
countCountries <- dataFinished[,3:3] %>% group_by(country)
countCountries <- countCountries[!duplicated(countCountries),] 
countCountries <- countCountries[order(countCountries$country),]
```

The provided data consists of $`r nrow(dataFinished)`$ different datasets from $`r nrow(countCountries)`$ different states. The data was set up into City, State, Country, Cost of Living Plus Rent Index, CLI, Rent Index, Groceries Index, Restaurant Index, Local Purchasing Power Index, Leverage Model 1 and Leverage Model 2 attributes.

```{r}
#| echo = FALSE,
#| warning = FALSE,
#| label = "worldMap",
#| fig.cap = "Industrialized and developing countries",
#| out.width = "80%",
#| fig.asp = 0.75,
#| fig.align = "center",


MapData <- dataFinished
#selecting attributes (country, development)
MapData <- MapData %>% select(3,13)
colnames(MapData)[1] <- "region"
#MapData <- MapData %>% group_by()
#merge data
world <- map_data("world")
MapData <- left_join(MapData, world, by="region")

plain <- theme(
  axis.text = element_blank(),
  axis.line = element_blank(),
  axis.ticks = element_blank(),
  panel.border = element_blank(),
  panel.grid = element_blank(),
  axis.title = element_blank(),
  panel.background = element_rect(fill = "white"),
  plot.title = element_text(hjust = 0.5)
)
worldDD <- ggplot(data = MapData, mapping = aes(x = long, y = lat, group = group)) +
  borders("world", fill="grey90",colour="grey") + 
  coord_fixed(1.3) +
  geom_polygon(aes(fill = development)) +
  scale_fill_distiller(palette ="RdBu", direction = 1) + # or direction=1
  #ggtitle("Industrialized and developing countries") +
  plain

worldDD

```


## Exploratory Data Analysis

First of all, we had to check, if there are missing values inside of the data-set. Therefore we used the following code to proof this:

```{r}
#| echo = TRUE,
#| message = TRUE
summary(is.na(dataFinished))
```
As it can be seen, there were $`r sum(is.na(dataFinished$state))`$ missing values inside the column "state". 
However, since the column has no bearing on our research question, we decided to disregard this column. With the city column we have a more meaningful basis to answer our question.
To disregard this column, we cut it off. To do this, we used to following R code chunk. Because it is the second column, we can just delete this column.

```{r}
#| echo = TRUE,
#| message = TRUE
dataFinished <- dataFinished[-2]
```

We also truncated the leverage_model_1 and leverage_model_2 columns, since we did not work with these columns any further.

```{r}
#| echo = TRUE,
#| message = TRUE
dataFinished <- dataFinished[-9]
dataFinished <- dataFinished[-9]
```

To determine if outliers exist within the data set, we chose to draw a boxplot.

```{r}
dataFinished %>%
  mutate(across(where(is.factor), as.numeric))
  
col = c('cost_of_living_plus_rent_index','cli','rent_index','groceries_index','restaurant_price_index','local_purchasing_power_index')
boxplot(dataFinished[,c('cost_of_living_plus_rent_index','cli','rent_index','groceries_index','restaurant_price_index','local_purchasing_power_index')])
```

--> TODO: Abbildung beschriften!

As can be seen from the figure, there are several outliers within the data set. In order not to distort the result, we decided to keep these outliers and to continue working with them.

--> TODO: Text zu Correlation schreiben

```{r}
datasummary_correlation(dataFinished)
```

## Folgendes nur zur Übersicht/weiteren Aufbau(Gliederung)

zu wrangling gehören joining, merging und grouping
Boxplot gehört zu profiling

3. Methods, for example:
- Descriptive statistics
- Variable distributions
- Statements about variances and co-variance and missing values
- Chosen analytical procedures to answer the research question


Inhalt/Aufbau:
  1:EDA (Exploratory Data Analysis) auf Datenset    anwenden
    1.1: including information on the variables’ distribution, missing values,
categories / grouping factors (if applicable) and the relationships between the variables, especially
regarding the variable in focus, for example, the dependent variable of a applied statistical method (if
applicable)
  2:Methoden/statistische Modelle aufstellen