---
output:
  pdf_document: default
  html_document: default
---
# Methods

## Setup
After the required libraries, which will be worked with in the following, were installed, the libraries still had to be imported in order to be able to use them.

```{r}
library(tidyverse)
library(dplyr)
library(stringr)
library(ggplot2)
library(maps)
library(janitor)
library(modelsummary)
library(car)
library(carData)
library(gpairs)
library(GGally)
```

Subsequently, the data had to be read in. This could be initialized with the following command, after the data set was added as a csv file in the folder "02-data".
To be able to work better with the names of the columns and the dataset in general, the command "janitor::clean_names" was executed.  With this, for example, the spaces were removed and the names were all written in small letters.

```{r}
rawData <- read_delim("02-data/cost-of-living-2017.csv", 
                      delim = "\t", escape_double = FALSE, 
                      trim_ws = TRUE)
rawData <- janitor::clean_names(rawData)
```

continents hinzufügen, damit das Datenset nach Regionen gefiltert werden kann

```{r}

```


## Exploratory Data Analysis

First of all, we had to check, if there are missing values inside of the data-set. Therefore we used the following code to proof this:

```{r}
#| echo = TRUE,
#| message = TRUE
summary(is.na(dataWithCategory))
```
As it can be seen, there were $`r sum(is.na(dataWithCategory$state))`$ missing values inside the column "state". 
However, since the column has no bearing on our research question, we decided to disregard this column. With the city column we have a more meaningful basis to answer our question.
To disregard this column, we cut it off. To do this, we used to following R code chunk. Because it is the second column, we can just delete this column.

```{r}
#| echo = TRUE,
#| message = TRUE
dataWithCategory <- dataWithCategory[-2]
```

We also truncated the leverage_model_1 and leverage_model_2 columns, since we did not work with these columns any further.

```{r}
#| echo = TRUE,
#| message = TRUE
dataWithCategory <- dataWithCategory[-9]
dataWithCategory <- dataWithCategory[-9]
```


## Folgendes nur zur Übersicht/weiteren Aufbau(Gliederung)

zu wrangling gehören joining, merging und grouping
Boxplot gehört zu profiling

3. Methods, for example:
- Descriptive statistics
- Variable distributions
- Statements about variances and co-variance and missing values
- Chosen analytical procedures to answer the research question


Inhalt/Aufbau:
  1:EDA (Exploratory Data Analysis) auf Datenset    anwenden
    1.1: including information on the variables’ distribution, missing values,
categories / grouping factors (if applicable) and the relationships between the variables, especially
regarding the variable in focus, for example, the dependent variable of a applied statistical method (if
applicable)
  2:Methoden/statistische Modelle aufstellen